% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.4in}  % Start text higher on the page 
\setlength{\textheight}{9.6in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Amogh Jalihal} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Amogh Prabhav Jalihal}
\address{C7-4, 5th Cross Road\\
IIT Campus, Chennai, 600036\\
amogh.jalihal@gmail.com}


\begin{resume}
%\vspace{0.1in}
%\moveleft.5\sectionwidth\centerline{Objective: Position as a summer intern.}  

\section{EDUCATION}
\vspace{0.1in} 
 
    \begin{tabular}{c c c c}
	\textbf{Class} & \textbf{Board/University} & \textbf{Marks obtained/GPA} & \textbf{Year of Passing} \\ 
 \hline \\
	10th Standard & CBSE & 94.0\% & 2009 \\ \\
	12th Standard & CBSE & 93.2\% & 2011 \\ \\
	First Year & SASTRA & 9.11 & 2012\\ \\
	Second Year & SASTRA & 9.05 & 2013 \\ \\ 
	Third Year & SASTRA & 8.78 & 2014 \\
\hline
 
	\end{tabular}

\section{Academic awards}
\vspace{0.1in}
Prize for the highest mark in Chemistry in 12th Board Examination.

Among the top 1.5\% of students who appeared for 12th Board Exam from Kendriya Vidyalaya Sangathan.

On the Dean's List for the first year (top 2\% for each year) and the second year (top 10\% for each year).


\section{Research Experience} 
\vspace{0.1in}
	%\begin{itemize}
{\bf 2010 summer:} Attended the Research Science Initiative 2010 organized by IIT Madras, based on a similar program conducted in MIT, USA. I gained lab experience in IIT Madras, in transformation experiments on bacteria, and the usage of various tools in genetic engineering.

{\bf 2012-present:} Carried out a project in the Quorum Sensing Lab in SASTRA, where I reviewed the virulence regulation in {\it Staphylococcus aureus} and created a boolean network for the same. Currently developing a cell interaction model to study behaviour of cell interaction networks in inter-species bacterial quorum sensing.

{\bf 2013 summer:} Worked as an intern in C-CAMP, Bangalore and learnt the use of High Pressure Liquid Chromatography (HPLC). Worked on a phytochemistry based drug discovery project.

{\bf 2014 summer:} Attended the NIGINTERN'14 program at the National Institute of Genetics, Japan for a 10 week internship in the Cell Architecture Lab. Worked on a microinjection project, along with data analysis involving images of HeLa cells undergoing mitosis. Learnt handling and genetic manipulation of {\it C.elegans}. 
 	%\end{itemize}

\section{International Conferences attended}
\vspace{0.1in}

{\bf 2013:} Computational neuroscience (From Hippocampus to Behaviour) held in IISER Pune, India in December 2013.

{\bf 2014:} {\it C. elegans} Asia-Pacific and Developmental Biology Conference held in Nara, Japan in July 2014.   

\pagebreak
\section{Research Interests}
\vspace{0.1in}

Dynamics involved in Meiotic as well as Mitotic cell division.

Design principles in developmental biology.

Stochastic Resonance in biological systems, specifically in quorum sensing and neural activity.

Modeling of large-scale behavior in mixed-species bacterial colonies with respect to interacting quorum-sensing circuits, at the population level.

Gene- and protein-interaction networks.

Non-linear dynamics in Biology.

\section{Computer Skills}
\vspace{0.1in}
{\textit {Operating Systems:}} Windows, Linux

{\textit {Programming languages:}} C, C++

{\textit {Scientific software:}} Scilab

{\textit {Documentation/Graphics:}} \LaTeX, GIMP
\section{Other Interests}
\vspace{0.1in}
Playing the tabla, active participant(acting, directing and script writing) in dramatics, keen interest in photography and image editing. 

Active interest in nature walks, bird watching and other outdoor activities.
 \end{resume}
\end{document}






























